Biomass trend maps

### 2019-06-25 analysis/VOCC/biomass-trends.Rmd
add ability to select different covariates and include these selections in file names

Species
```{r}
species <- "Quillback Rockfish"
species <- "Yelloweye Rockfish"
species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
species <- "Silvergray Rockfish"
species <- "Arrowtooth Flounder"
species <- "Lingcod"

@@

# folder to hold figs for this species
dir.create(file.path("figs", spp))
dir.create(file.path("data", spp))
```

Is a new spatial needed?
```{r}
update_spatial_model <- TRUE
priors <- FALSE
# priors <- TRUE

# Choose region to update model for:

region <- "Both odd year surveys"
region <- "West Coast Vancouver Island"
region <- "West Coast Haida Gwaii"

# region <- "Queen Charlotte Sound"
# region <- "Hecate Strait"
# region <- "Both West Coast surveys"
```

If not...
```{r}
update_spatial_model <- FALSE
priors <- FALSE
# priors <- TRUE
region <- "All synoptic surveys" 
```

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```

@@

# if(region == "Queen Charlotte Sound") {
# survey <- c("SYN QCS")
# model_ssid <- c(1)
# ssid_string <- paste0(model_ssid, collapse = "n")
# years <- NULL
# }
#
# if(region == "Hecate Strait") {
# survey <- c("SYN HS")
# model_ssid <- c(3)
# ssid_string <- paste0(model_ssid, collapse = "n")
# years <- NULL
# }

# if(region == "Both West Coast surveys") {
# survey <- c("SYN WCVI","SYN WCHG")
# model_ssid <- c(4,16)
# years <- NULL
# }

@@

  newcov <- readRDS("data/new_covariates.rds") %>% dplyr::select(X, Y, trawled, muddy, rocky)
  nd_all <- left_join(nd_all, newcov, by=c("X", "Y"))

@@

  maturity <- split_catch_maturity(survey_sets, fish, bath,
    # survey = c("SYN QCS","SYN HS","SYN WCVI","SYN WCHG"),
    survey = c("SYN HS", "SYN WCHG"),
    #  survey = survey,
    years = years,
    cutoff_quantile = c(.9995),
    plot = TRUE
  )

@@

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
if (update_spatial_model) {
  biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds"))
  covars <- readRDS("data/event-covariates.rds")
  data <- dplyr::left_join(biomass,covars)

@@

  if (any(names(data) == "adult_density")) {
    starttime1 <- Sys.time()
    adult_biomass <- sdmTMB::sdmTMB(data,
      adult_density ~ 0 + as.factor(year) + trawled + muddy + rocky,
      time_varying = ~ 0 + depth_scaled + depth_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime1 <- Sys.time()
    time1 <- round(starttime1 - endtime1)

    saveRDS(adult_biomass, file = paste0("data/", spp, "/model-mature-biomass-", spp, "-", ssid_string, "-priors-", priors, time1, "-newcovs.rds"))

    starttime2 <- Sys.time()
    imm_biomass <- sdmTMB::sdmTMB(data,
      imm_density ~ 0 + as.factor(year) + trawled + muddy + rocky,
      time_varying = ~ 0 + depth_scaled + depth_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = FALSE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime2 <- Sys.time()
    time2 <- round(starttime2 - endtime2)

    saveRDS(imm_biomass, file = paste0("data/", spp, "/model-imm-biomass-", spp, "-", ssid_string, "-priors-", priors, time2, "-newcovs.rds"))
  } else {
    starttime3 <- Sys.time()
    total_biomass <- sdmTMB::sdmTMB(dat,
      density ~ 0 + as.factor(year)+ trawled + muddy + rocky,
      time_varying = ~ 0 + depth_scaled + depth_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE, ,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime3 <- Sys.time()
    time3 <- round(starttime3 - endtime3)

    saveRDS(total_biomass, file = paste0("data/", spp, "/model-total-biomass-", spp, "-", ssid_string, "-priors-", priors, "-newcovs.rds"))
  }
}
```

@@

if (isFALSE(update_spatial_model)) {
  if (region != "All synoptic surveys") {
    try(adult_predictions <- readRDS(paste0("data/", spp, "/predictions-", spp, "-", ssid_string, "-mature-biomass-priors-", priors, ".rds")))
    try(imm_predictions <- readRDS(paste0("data/", spp, "/predictions-", spp, "-", ssid_string, "-imm-biomass-priors-", priors, ".rds")))
    try(predictions <- readRDS(paste0("data/", spp, "/predictions-", spp, "-", ssid_string, "-total-biomass-priors-", priors, ".rds")))
  } else {
    # Bind together predictions from different models
    try ({
      pred1n3 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-mature-biomass-priors-", priors, ".rds"))
      pred4 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-mature-biomass-priors-", priors, ".rds"))
      pred16 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-mature-biomass-priors-", priors, ".rds"))
      adult_predictions <- rbind(pred1n3, pred4, pred16) 
      # model_ssid <- unique(adult_predictions$ssid)
      # ssid_string <- paste0(model_ssid, collapse = "n")
    })

    try ({
      pred1n3_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-imm-biomass-priors-", priors, ".rds"))
      pred4_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-imm-biomass-priors-", priors, ".rds"))
      pred16_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-imm-biomass-priors-", priors, ".rds"))
      imm_predictions <- rbind(pred1n3_imm, pred4_imm, pred16_imm) 
      # model_ssid <- unique(imm_predictions$ssid)
      # ssid_string <- paste0(model_ssid, collapse = "n")
    })

    try ({
      pred1n3_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-total-biomass-priors-", priors, ".rds"))
      pred4_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-total-biomass-priors-", priors, ".rds"))
      pred16_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-total-biomass-priors-", priors, ".rds"))
      predictions <- rbind(pred1n3_all, pred4_all, pred16_all) # ,
      #  model_ssid <- unique(predictions$ssid),
      # ssid_string <- paste0(model_ssid, collapse = "n")
    })

@@

if (!exists("adult_predictions")) {
  if (length(unique(fish$maturity_code)) > 2) {
    nd_all <- readRDS(paste0("data/nd_all_synoptic.rds"))
    nd <- nd_all %>% filter(ssid %in% model_ssid) 
    nd <- na.omit(nd)
    nd$year <- as.integer(nd$year)

    adult_biomass <- readRDS(list.files(
      path = paste0("data/", spp, "/"),
      pattern = paste0("model-mature-biomass-", spp, "-", ssid_string, "-priors-", priors, "-*"),
      all.files = F, full.names = T
    ))

    adult_predictions <- predict(adult_biomass, newdata = nd)
    saveRDS(adult_predictions,
      file = paste0("data/", spp, "/predictions-", spp, "-", ssid_string, "-mature-biomass-priors-", priors, ".rds")
    )

    imm_biomass <- readRDS(list.files(
      path = paste0("data/", spp, "/"),
      pattern = paste0("model-imm-biomass-", spp, "-", ssid_string, "-priors-", priors, "-*"),
      all.files = F, full.names = T
    ))
    imm_predictions <- predict(imm_biomass, newdata = nd)
    saveRDS(imm_predictions,
      file = paste0("data/", spp, "/predictions-", spp, "-", ssid_string, "-imm-biomass-priors-", priors, ".rds")
    )
  } else {
    rm(adult_predictions)
    rm(imm_predictions)

@@

      total_biomass <- readRDS(paste0("data/", spp, "/model-total-biomass-", spp, "-", ssid_string, "-priors-", priors, ".rds"))
      nd$year <- as.integer(nd$year)
      predictions <- predict(total_biomass, newdata = nd)
      saveRDS(predictions, file = paste0("data/", spp, "/predictions-", spp, "-", ssid_string, "-total-biomass-priors-", priors, ".rds"))
    }
  }
}
```

Bind together predictions from different models
```{r, eval=FALSE}
if (region == "All synoptic surveys") {
  if (isFALSE(update_spatial_model)) {
    try(
      pred1n3 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-mature-biomass-priors-", priors, ".rds")),
      pred4 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-mature-biomass-priors-", priors, ".rds")),
      pred16 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-mature-biomass-priors-", priors, ".rds")),

@@

    try(
      pred1n3_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-imm-biomass-priors-", priors, ".rds")),
      pred4_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-imm-biomass-priors-", priors, ".rds")),
      pred16_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-imm-biomass-priors-", priors, ".rds")),

@@

    try(
      pred1n3_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-total-biomass-priors-", priors, ".rds")),
      pred4_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-total-biomass-priors-", priors, ".rds")),
      pred16_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-total-biomass-priors-", priors, ".rds")),

@@

  max_raster <- quantile(adult_predictions$est_exp, .9999)
  max_adult <- round(max(adult_predictions$est_exp))
} else {
  predictions$total_bio <- exp(predictions$est) * 10000
  max_raster <- quantile(predictions$total_bio, .9999)
  max_bio <- round(max(predictions$total_bio))
}
```

```{r, error=TRUE}
if (exists("adult_predictions")) {
  p_adult_all <- plot_facet_map(adult_predictions, "est_exp",
    transform_col = fourth_root_power,
    raster_limits = c(0, max_raster),
    legend_position = "none"
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))
  print(p_adult_all)
} else {
  p_adult_all <- plot_facet_map(predictions, "total_bio",
    # raster_limits = c(0, max_raster),
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))
  print(p_adult_all)
}
```

@@

saveRDS(out_mature,
  file = paste0("data/", spp, "/trends-", spp, "-", ssid_string, "-mature-biomass-priors-", priors, ".rds")
)

if (!exists("adult_predictions")) {
  out_total <- out_mature
  saveRDS(out_total,
    file = paste0("data/", spp, "/trends-", spp, "-", ssid_string, "-total-biomass-priors-", priors, ".rds")
  )
}
```

@@

```{r, error=TRUE}
try(out_mature <- readRDS(paste0("data/", spp, "/trends-", spp, "-", ssid_string, "-mature-biomass-priors-", priors, ".rds")))

if (exists("out_mature")) {
  data <- out_mature
  biotrend_ad <- plot_vocc(data,
    fill_col = "units_per_decade",
    fill_label = "Mature \nbiomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    # axis_lables = TRUE,
    white_zero = TRUE,
    transform_col = fourth_root_power,
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0("", species, " ", min(unique(adult_predictions[["year"]])), "-", max(unique(adult_predictions[["year"]]))))
  biotrend_ad
} else {
  try(out_total <- readRDS(paste0("data/", spp, "/trends-", spp, "-", ssid_string, "-total-biomass-priors-", priors, ".rds")))

@@

  out_imm <- rbind(out_im1, out_im3, out_im4, out_im16)
  saveRDS(out_imm,
    file = paste0("data/", spp, "/trends-", spp, "-", ssid_string, "-immature-biomass-priors-", priors, ".rds")
  )
} else {
  rm(out_imm)
}
```

```{r}
try(out_imm <- readRDS(paste0("data/", spp, "/trends-", spp, "-", ssid_string, "-immature-biomass-priors-", priors, ".rds")))

@@

```{r}
png(
  file = paste0("figs/", spp, "/trends-", spp, "-", ssid_string, "-priors-", priors, ".png"), # The directory you want to save the file in
  res = 600,
  units = "in",
  width = 11, # The width of the plot in inches
  height = 8
)
gridExtra::grid.arrange(
  # p_adult, p_imm,
  biotrend_ad, biotrend_im,
  nrow = 1
)
dev.off()
```

@@

png(
  file = paste0("figs/", spp, "/biomass-", spp, "-", ssid_string, "-priors-", priors, ".png"), # The directory you want to save the file in
  res = 600,
  units = "in",
  width = 16, # The width of the plot in inches
  height = 8.5
)
gridExtra::grid.arrange(
  grobs = biomass_plots,
  nrow = 2
)
dev.off()
```

```{r}
png(
  file = paste0("figs/", spp, "/exploratory-", spp, "-", ssid_string, "-priors-", priors, ".png"), # The directory you want to save the file in
  res = 600,
  units = "in",
  width = 9.5, # The width of the plot in inches
  height = 12.5
) # The height of the plot in inches

>>>>

Species
```{r}
species <- "Quillback Rockfish"
# species <- "Yelloweye Rockfish"
# priors <- TRUE
covariates <- "+trawled+mixed+rocky"

species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
species <- "Silvergray Rockfish"
species <- "Arrowtooth Flounder"
species <- "Lingcod"
```

# Choose covariates  
```{r}
covariates <- "+trawled+muddy+rocky+mixed"
covariates <- "+trawled+mixed+rocky"
covariates <- "+muddy+mixed+rocky"
covariates <- "+mixed+rocky"
covariates <- "+trawled+mixed"
```

Is a new spatial needed?
```{r}
update_spatial_model <- TRUE
priors <- FALSE
#priors <- TRUE

# Choose region to update model for:
region <- "Both odd year surveys"
region <- "West Coast Vancouver Island"
region <- "West Coast Haida Gwaii"

```

If not...
```{r}
update_spatial_model <- FALSE
priors <- FALSE
# priors <- TRUE
region <- "All synoptic surveys"

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)

@@

# folder to hold figs for this species
dir.create(file.path("figs", spp))
dir.create(file.path("data", spp))
fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

```

# if(region == "Queen Charlotte Sound") {
# survey <- c("SYN QCS")
# model_ssid <- c(1)
# ssid_string <- paste0(model_ssid, collapse = "n")
# years <- NULL
# }
#
# if(region == "Hecate Strait") {
# survey <- c("SYN HS")
# model_ssid <- c(3)
# ssid_string <- paste0(model_ssid, collapse = "n")
# years <- NULL
# }
```

@@

  newcov <- readRDS("data/new_covariates.rds") %>% dplyr::select(X, Y, trawled, muddy, rocky, mixed)
  nd_all <- left_join(nd_all, newcov, by=c("X", "Y"))

@@

  maturity <- split_catch_maturity(survey_sets, fish, bath,
    # survey = c("SYN QCS","SYN HS","SYN WCVI","SYN WCHG"),
    # survey = c("SYN HS", "SYN WCHG"),
    survey = survey,
    years = years,
    cutoff_quantile = c(.9995),
    plot = TRUE
  )

@@

Run sdmTMB model (if not done previously).
```{r}
if (update_spatial_model) {
  biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds"))
  covars <- readRDS("data/event-covariates.rds")
  data <- dplyr::left_join(biomass,covars)

@@

  if (any(names(data) == "adult_density")) {

    adult_formula <- as.formula(paste("adult_density ~ 0 + as.factor(year)", covariates, ""))

    starttime1 <- Sys.time()
    adult_biomass <- sdmTMB::sdmTMB(data,
      adult_formula,
      time_varying = ~ 0 + depth_scaled + depth_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime1 <- Sys.time()
    time1 <- round(starttime1 - endtime1)

    saveRDS(adult_biomass, file = paste0("data/", spp, "/mod-mat-biomass-", spp, covariates, "-", ssid_string, "-prior-", priors, time1, ".rds"))

    imm_formula <- as.formula(paste("imm_density ~ 0 + as.factor(year)", covariates, ""))

    starttime2 <- Sys.time()
    imm_biomass <- sdmTMB::sdmTMB(data, 
      imm_formula,
      time_varying = ~ 0 + depth_scaled + depth_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = FALSE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime2 <- Sys.time()
    time2 <- round(starttime2 - endtime2)

    saveRDS(imm_biomass, file = paste0("data/", spp, "/mod-imm-biomass-", spp, covariates, "-", ssid_string, "-prior-", priors, time2, ".rds"))
  } else {
    starttime3 <- Sys.time()
    dens_formula <- as.formula(paste("density ~ 0 + as.factor(year)", covariates, ""))

    total_biomass <- sdmTMB::sdmTMB(dat,
      dens_formula,
      time_varying = ~ 0 + depth_scaled + depth_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime3 <- Sys.time()
    time3 <- round(starttime3 - endtime3)

    saveRDS(total_biomass, file = paste0("data/", spp, "/model-total-biomass-", spp, covariates, "-", ssid_string, "-prior-", priors, ".rds"))
  }
}
```

@@

if (isFALSE(update_spatial_model)) {
  if (region != "All synoptic surveys") {
    try(adult_predictions <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-", ssid_string, "-mature-biomass-prior-", priors, ".rds")))
    try(imm_predictions <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-", ssid_string, "-imm-biomass-prior-", priors, ".rds")))
    try(predictions <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-", ssid_string, "-total-biomass-prior-", priors, ".rds")))
  } else {
    # Bind together predictions from different models
    try ({
      pred1n3 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-mature-biomass-prior-", priors, ".rds"))
      pred4 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-mature-biomass-prior-", priors, ".rds"))
      pred16 <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-mature-biomass-prior-", priors, ".rds"))
      adult_predictions <- rbind(pred1n3, pred4, pred16) 
      # model_ssid <- unique(adult_predictions$ssid)
      # ssid_string <- paste0(model_ssid, collapse = "n")
    })

    try ({
      pred1n3_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-imm-biomass-prior-", priors, ".rds"))
      pred4_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-imm-biomass-prior-", priors, ".rds"))
      pred16_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-imm-biomass-prior-", priors, ".rds"))
      imm_predictions <- rbind(pred1n3_imm, pred4_imm, pred16_imm) 
      # model_ssid <- unique(imm_predictions$ssid)
      # ssid_string <- paste0(model_ssid, collapse = "n")
    })

    try ({
      pred1n3_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-total-biomass-prior-", priors, ".rds"))
      pred4_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-total-biomass-prior-", priors, ".rds"))
      pred16_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-total-biomass-prior-", priors, ".rds"))
      predictions <- rbind(pred1n3_all, pred4_all, pred16_all) # ,
      #  model_ssid <- unique(predictions$ssid),
      # ssid_string <- paste0(model_ssid, collapse = "n")
    })

@@

if (!exists("adult_predictions")) {
    fish <- readRDS(paste0("raw/bio-data-", spp, ""))

  if (length(unique(fish$maturity_code)) > 2) {

    adult_biomass <- readRDS(list.files(
      path = paste0("data/", spp, "/"),
      #pattern = paste0("mod-mat-biomass-", spp, "-", ssid_string, "-prior-", priors, "-*"),
      pattern = paste0("mod-mat-biomass-", spp, covariates, "-", ssid_string, "-prior-", priors, "-*"),
      all.files = F, full.names = T
    ))

    nd_all <- readRDS(paste0("data/nd_all_synoptic.rds"))
    nd <- nd_all %>% filter(ssid %in% model_ssid) %>% filter(year %in% unique(adult_biomass$data$year))
    nd <- na.omit(nd)
    nd$year <- as.integer(nd$year)

    adult_predictions <- predict(adult_biomass, newdata = nd)
    saveRDS(adult_predictions,
      file = paste0("data/", spp, "/predictions-", spp, covariates,"-", ssid_string, "-mature-biomass-prior-", priors, ".rds")
    )

    imm_biomass <- readRDS(list.files(
      path = paste0("data/", spp, "/"),
      #pattern = paste0("model-imm-biomass-", spp, "-", ssid_string, "-prior-", priors, "-*"),
      pattern = paste0("mod-imm-biomass-", spp, covariates, "-", ssid_string, "-prior-", priors, "-*"),
      all.files = F, full.names = T
    ))
    imm_predictions <- predict(imm_biomass, newdata = nd)
    saveRDS(imm_predictions,
      file = paste0("data/", spp, "/predictions-", spp, covariates,"-", ssid_string, "-imm-biomass-prior-", priors, ".rds")
    )
  } else {
    rm(adult_predictions)
    rm(imm_predictions)

@@

      total_biomass <- readRDS(paste0("data/", spp, "/model-total-biomass-", spp, covariates, "-", ssid_string, "-prior-", priors, ".rds"))
      nd$year <- as.integer(nd$year)
      predictions <- predict(total_biomass, newdata = nd)
      saveRDS(predictions, file = paste0("data/", spp, "/predictions-", spp, covariates,"-", ssid_string, "-total-biomass-prior-", priors, ".rds"))
    }
  }
}
```

Bind together predictions from different models
```{r, eval=FALSE}
if (region == "All synoptic surveys") {
  if (isFALSE(update_spatial_model)) {
    try(
      pred1n3 <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-1n3-mature-biomass-prior-", priors, ".rds")),
      pred4 <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-4-mature-biomass-prior-", priors, ".rds")),
      pred16 <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-16-mature-biomass-prior-", priors, ".rds")),

@@

    try(
      pred1n3_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-1n3-imm-biomass-prior-", priors, ".rds")),
      pred4_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-4-imm-biomass-prior-", priors, ".rds")),
      pred16_imm <- readRDS(paste0("data/", spp, "/predictions-", spp, covariates, "-16-imm-biomass-prior-", priors, ".rds")),

@@

    try(
      pred1n3_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-1n3-total-biomass-prior-", priors, ".rds")),
      pred4_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-4-total-biomass-prior-", priors, ".rds")),
      pred16_all <- readRDS(paste0("data/", spp, "/predictions-", spp, "-16-total-biomass-prior-", priors, ".rds")),

@@

  max_raster <- quantile(adult_predictions$est_exp, .9999)
  max_adult <- signif(max(adult_predictions$est_exp), digits = 2)
} else {
  predictions$total_bio <- exp(predictions$est) * 10000
  max_raster <- quantile(predictions$total_bio, .9999)
  max_bio <- round(max(predictions$total_bio))
}
```

```{r, error=TRUE}
if (exists("adult_predictions")) {
  p_adult_all <- plot_facet_map(adult_predictions, "est_exp",
    raster_limits = c(0, max_raster),
    legend_position = "none",
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))
  print(p_adult_all)
} else {
  p_adult_all <- plot_facet_map(predictions, "total_bio",
    # raster_limits = c(0, max_raster),
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))
  print(p_adult_all)
}
```

@@

saveRDS(out_mature,
  file = paste0("data/", spp, "/trends-", spp, covariates, "-", ssid_string, "-mature-biomass-priors-", priors, ".rds")
)

if (!exists("adult_predictions")) {
  out_total <- out_mature
  saveRDS(out_total,
    file = paste0("data/", spp, "/trends-", spp, covariates, "-", ssid_string, "-total-biomass-priors-", priors, ".rds")
  )
}
```

@@

```{r, error=TRUE}
try(out_mature <- readRDS(paste0("data/", spp, "/trends-", spp, covariates, "-", ssid_string, "-mature-biomass-priors-", priors, ".rds")))

if (exists("out_mature")) {
  data <- out_mature
  biotrend_ad <- plot_vocc(data,
    fill_col = "units_per_decade",
    fill_label = "Mature \nbiomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    # axis_lables = TRUE,
    white_zero = TRUE,
    transform_col = fourth_root_power,
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0("", species, " ", min(unique(adult_predictions[["year"]])), "-", max(unique(adult_predictions[["year"]]))))
  biotrend_ad
} else {
  try(out_total <- readRDS(paste0("data/", spp, "/trends-", spp, covariates, "-", ssid_string, "-total-biomass-priors-", priors, ".rds")))

@@

  out_imm <- rbind(out_im1, out_im3, out_im4, out_im16)
  saveRDS(out_imm,
    file = paste0("data/", spp, "/trends-", spp, covariates, "-", ssid_string, "-immature-biomass-priors-", priors, ".rds")
  )
} else {
  rm(out_imm)
}
```

```{r}
try(out_imm <- readRDS(paste0("data/", spp, "/trends-", spp, covariates, "-", ssid_string, "-immature-biomass-priors-", priors, ".rds")))

@@

```{r}
png(
  file = paste0("figs/", spp, "/trends-", spp, covariates, "-", ssid_string, "-priors-", priors, ".png"), # The directory you want to save the file in
  res = 600,
  units = "in",
  width = 11, # The width of the plot in inches
  height = 8
)
gridExtra::grid.arrange(
  # p_adult, p_imm,
  biotrend_ad, biotrend_im,
  nrow = 1
)
dev.off()
```

@@

png(
  file = paste0("figs/", spp, "/biomass-", spp, covariates, "-", ssid_string, "-priors-", priors, ".png"), # The directory you want to save the file in
  res = 600,
  units = "in",
  width = 16, # The width of the plot in inches
  height = 8.5
)
gridExtra::grid.arrange(
  grobs = biomass_plots,
  nrow = 2
)
dev.off()
```

```{r}
png(
  file = paste0("figs/", spp, "/exploratory-", spp, covariates, "-", ssid_string, "-priors-", priors, ".png"), # The directory you want to save the file in
  res = 600,
  units = "in",
  width = 9.5, # The width of the plot in inches
  height = 12.5
) # The height of the plot in inches
